\problemname{Lava Kayaking}

Lav has been captured by an evil witch in a volcano. In the vast lava sea of the volcano, there are $N$ islands in a long row.
The distance between the $i$:th and the $(i+1)$:th island is $d_i$. The distances are given in the unit
”witchameter,” which corresponds to exactly $H$ meters. The witch lives on the first island in the row,
and this is where Lav is currently located.

The witch has forgotten her book with all the spells on the last island in the row, and now forces Lav
to go and fetch it. To help him, he has a lava boat and a number of paddles.
Each paddle lasts for $K$ paddle strokes, where each stroke moves the boat forward one meter, before
the paddle burns up due to the lava.
Lav takes a number of paddles from the witch and does not need to completely use up one paddle before switching to another.

Additionally, Lav has a spell from the witch that he can use when he is on an island. The spell repairs
a paddle that he has paddled with a bit but hasn't completely burned up.
He can then use it again to paddle $K$ meters. Lav can use the spell as many times as he wants when he is on an island.

Write a program that calculates the minimum number of paddles the witch needs to give Lav so that he can complete the mission.


\section*{Input}
The first line contains the integers $N, K, H$ ($1 \leq N \leq 20, 1 \leq K \leq 15, 1 \leq H \leq 10^{12}$),
the number of islands, the number of meters you can paddle with a paddle before it burns up, and the number of meters a witchameter corresponds to.

The second line contains $N-1$ integers $d_i$ ($1 \leq d_i \leq 1000$), the distances between adjacent islands in the row.

\section*{Output}
Print an integer: the minimum number of paddles the witch needs to give Lav so that he can complete the mission.

\section*{Points}
Your solution will be tested on several test case groups.
To get the points for a group, it must pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$    & $20$        &  $ K = 1, H \leq 100 $ \\ \hline 
  $2$    & $40$        &  $ H = 1 $ \\ \hline
  $3$    & $40$        &  No additional constraints. \\ \hline
\end{tabular}



\section*{Explanation of samples}
In the first example, there are two islands, with a distance of $7$ witchameters, which corresponds to
$7\cdot H = 7\cdot 10=70$ meters. With each paddle, he can take a maximum of $5$ paddle strokes, so
$70/5 = 14$ paddles are required.

In the second example, there are three islands, with $200$ meters between the first and the second, and
$100$ meters between the second and the third. Each paddle can take $7$ paddle strokes. If Lav starts
with $31$ paddles, uses $14$ of them fully, and takes $6$ paddle strokes with the remaining $17$ paddles,
he will cover $14\cdot 7+6\cdot 17=200$ meters, enough to reach the second island. Then he has $17$ paddles
left, which he repairs with the spell, enough to get from the second to the third island. It would not
have been possible with fewer than $31$ paddles.

