\problemname{Vaccines}

Fredrika and her friends are eagerly waiting for their COVID-19 vaccine. They are so anxious to
know when they will get their vaccine that they have obtained classified information from the
government about the vaccination process. Specifically, they know that there are $p_i$ people
ahead of friend $i$ in the queue, and they know how many people get vaccinated each day. Help
them calculate when Fredrika and each of her friends will be vaccinated.


\section*{Input}
The first line contains two integers $N$ and $Q$ ($1 \leq N, Q \leq 10^5$), the number of days
where they know how many people get vaccinated, and the number of friends, including Fredrika,
who want to know when they will get their vaccine.

The next line contains $N$ integers $0 \leq k_j \leq 15$, the number of people who get vaccinated on day $j$ ($1 \leq j \leq N$).

Then follows a line with $Q$ integers $0 \leq p_i \leq 10^6$, the number of people ahead of friend $i$ in the queue.

\section*{Output}
For each of the $Q$ people, print a line with the day when they will be vaccinated. 
If someone is so far back in the queue that you don't know when they will be vaccinated, print $-1$.

\section*{Points}
Your solution will be tested on several test case groups.
To get the points for a group, it must pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$    & $50$      & $Q=1$, $N \le 100$ \\ \hline
  $2$    & $50$      & No additional constraints. \\ \hline
\end{tabular}

%\section*{Samples}
