\problemname{Squirrel In A Tree}

A squirrel lives in a tree with $N$ nodes and $N-1$ edges.
Each edge has a length of 1 and connects two nodes.
In some of the nodes, the squirrel has hidden nuts, which he now wants to collect.
If the squirrel starts at node $1$ (the root of the tree),
what is the shortest distance he needs to travel to collect all the nuts and return to node $1$?
The squirrel can carry multiple nuts at the same time.

It is guaranteed that it is possible to travel between all pairs of nodes via a sequence of edges.


\section*{Input}
The first line contains two integers $N$ and $K$ ($1 \leq K \leq N \leq 10^5$), the number of nodes
in the tree and the number of nodes with nuts.

The second line contains $K$ unique integers -- the nodes where the squirrel has hidden nuts. The nodes are indexed from 1 to $N$.

Then follow $N-1$ lines. Each line contains two integers $a,b$ ($1 \leq a, b \leq N$) which means that there
is an edge between node $a$ and node $b$.

\section*{Output}
Print an integer: the shortest distance the squirrel needs to travel to collect all its nuts.

\section*{Points}
Your solution will be tested on several test case groups.
To get the points for a group, it must pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$    & $20$        &  The $i$:th edge connects node $i$ and $i+1$ for all $1\le i \le N-1$ \\ \hline 
  $2$    & $40$        &  $1 \le K \le N \le 1000$ \\ \hline
  $3$    & $40$        &  No additional constraints. \\ \hline
\end{tabular}

%\section*{Samples}
