\problemname{Drone Flying}

You have just gotten a new battery-powered drone, but you lack batteries.
In the store, there are $N$ batteries available for the drone,
each with an energy $e_i$, weight $w_i$, and cost $c_i$.
The store has only one of each battery.

To have as much fun as possible with the drone, you obviously want it to
fly as long as possible on a full charge.
The time the drone can stay in the air is given by the expression $t = \frac{E_{tot}}{W_{tot}}$ where $E_{tot}$
is the total energy content of all the drone's batteries, and $W_{tot}$ is the combined weight of the drone and the batteries.

Given a budget $B$ and the weight of the drone itself $W$, determine
the maximum time the drone can fly.


\section*{Input}
The first line contains three integers $N$, $B$, and $W$ ($1 \leq N \times B \leq 200,000$ and $1 \leq W \leq 1000$),
the number of available batteries, your budget, and the weight of the drone.

The following $N$ lines each contain three integers. Line number $i$ contains $e_i$,
$w_i$, and $c_i$ ($0 \leq e_i \leq 1000$, $0 \leq w_i \leq 1000$, $0 \leq c_i \leq B$), 
the energy, weight, and cost of battery $i$.

\section*{Output}
Print a decimal number: The longest time you can fly your drone if you choose the batteries optimally.
The answer will be accepted if it has a relative or absolute error of at most $10^{-5}$.
That is, if your answer is $a$ and the correct answer is $b$, your answer will be accepted if
either $|a-b| \leq 10^{-5}$ or $\frac{|a-b|}{|b|} \leq 10^{-5}$.

\section*{Points}
Your solution will be tested on several test case groups.
To get the points for a group, it must pass all the test cases in the group.

\noindent
\begin{tabular}{| l | l | p{12cm} |}
  \hline
  \textbf{Group} & \textbf{Point value} & \textbf{Constraints} \\ \hline
  $1$   & $10$       & $N \leq 20$ \\ \hline
  $2$   & $20$       & $w_i = 0$ \\ \hline
  $3$   & $20$       & $c_1 = c_2 = \dots = c_N$ \\ \hline
  $4$   & $50$       & No additional constraints. \\ \hline
\end{tabular}

%\section*{Samples}
