\problemname{Reinventing Mathematics}

Oh no, all mathematics has disappeared! How did this happen? You don't have time to ponder over it,
instead you realize that you must reinvent as much mathematics as possible before the world ends!
Although all actual knowledge has vanished, you know a little about mathematics.
Mathematics is composed of $N$ theorems. Each theorem, $i$, depends on a number of theorems
$a_{i_1}, a_{i_2}, \cdots, a_{i_k} < i$, which must be proven before one can start with the theorem.
To prove theorem $i$ you need to spend $t_i$ time. The value of a proven theorem is $v_i$.

You have $T$ time. Choose which theorems you should prove to maximize the total value of the mathematics you have time to reinvent.


\section*{Input}
The first line contains an integer $C$ ($0 \leq C \leq 10$), the number of the test case ($0$ is the example case below).

The second line contains two integers: $N$ ($1 \le N \le 10^5$) and $T$ ($1 \le T \le 10^7$).

Then follows $N$ descriptions of theorems.
A description of a theorem consists of two rows. First comes a row with the integers $t_i, v_i$ and $k_i$
($0 \le t_i, v_i \le 10^4$, $0 \le k_i \le N$).
Then comes a row with $k_i$ integers: $a_{i_1}, a_{i_2}, \cdots, a_{i_k} < i$, the indices of the theorems that
must be proven before this theorem.
Theorems are indexed from 0 in the order they appear in the input.

\section*{Output}
First print an integer $S$ ($0 \leq S \leq N$), the number of theorems that you will prove.

On the next line, print $S$ integers, the theorems that you will prove in the order that you will prove them.

\section*{Points}
Your program will be tested on $10$ test cases and scored based on how it performs relative to the judges' solution.
If your submission on a given test case achieves a total value of theorems equal to $X$, and the total value the
judges have achieved on that test case is $Y$,
then your score on that test case will be $min(10, 10 \cdot (X / Y)^3)$, rounded to two decimal places.

Your score for a submission is the sum of the scores for the test cases, and your total score is the score for the best submission.
Thus, it is not possible to combine test cases between different submissions; instead, you must submit a single program that
maximizes your score on all test cases simultaneously.

The example test case will always give $0$ points.

\section*{Test cases}
Under attachments at the bottom of the page, you can download testcases generated in the same way as the real
testcases, but using a different \href{https://en.wikipedia.org/wiki/Random_seed}{random seed}.

The $10$ testcases are described below.

\noindent
\begin{tabular}{| l | l | l |}
\hline
\textbf{Testcase} & \textbf{Constraints}  \\ \hline
$1$       & $N=500,T=5000,k_i \le 3$  \\ \hline
$2$       & $N=500,T=5000,k_i \le 30$  \\ \hline
$3$       & $N=500,T=50000,k_i \le 3$  \\ \hline
$4$       & $N=500,T=50000,k_i \le 30$  \\ \hline
$5$       & $N=10^5,T=10^7,k_i \le 3$  \\ \hline
$6$       & $N=10^5,T=10^7,k_i \le 30$  \\ \hline
$7$       & $N=300,T=30000$ and $k_i=1$ for all $i \neq 0$. \\ \hline
$8$       & $N=300,T=30000$ and every theorem is needed to prove at most one other theorem. \\ \hline
$9$       & $N=10^5,T=10^7$ and $k_i=1$ for all $i \neq 0$. \\ \hline
$10$      & $N=10^5,T=10^7$ and every theorem is needed to prove at most one other theorem.  \\ \hline
\end{tabular}
